### 2017-07-19 background.tex
minor mods

The workflow of an analyst on \NAME involves requesting access to a dataset, submitting analysis
tasks via the various interfaces to interrogate the data and tune the analysis until results are generated.
These results are available by accessing a unique URL for the submitted task and are not tied to any user.
This was designed to allow for sharing of analysis codes and results, but it also introduces the risk
of unintended, unapproved access to the generated results. More importantly since there is no disclosure
controls on the results generated, any sensitive data that is included in results can be exported.
In this paper we describe how we have extended this security model to support the most sensitive datasets
that require stringent oversight with respect to data access access and export.

>>>>

The workflow of an analyst on \NAME involves requesting access to a dataset, submitting analysis
tasks via the various interfaces \cite{babuji2017enabling} to interrogate the data and tune the analysis until results are generated.
These results are available by accessing a unique URL for the submitted task and are not tied to any user.
This was designed to allow for sharing of analysis codes and results, but it also introduces the risk
of unintended, unapproved access to the generated results. More importantly since there is no disclosure
controls on the results generated, any sensitive data that is included in results can be exported.
In this paper we describe how we have extended this security model to support the most sensitive datasets
that require stringent oversight with respect to data access access and export.
